From heartbeat to data – Using wearable fitness trackers as an affordable approach to assess teacher stress

### 2024-10-03 02_paper/02_study/01_fitbit paper/Submission/FitBit_submission_template.Rmd
affiliationen angepasst

    state: Sachsen
    postcode: 04109

@@

    postcode: 04103

@@

    state: Sachsen

@@

    state: Mecklenburg-Vorpommern
    postcode: 17489  

@@

    text: 
      - "Conceptualization, Methodology, Formal analysis, Investigation, Data Curation, Writing - Original Draft"

@@

    text: 
      - "Conceptualization, Methodology, Writing - Review & Editing, Supervision"

@@

\begin{table}[ht]
    \centering
    \begin{tabularx}{\textwidth}{lXXXXXX}
        \toprule
        Interval  & \multicolumn{2}{c}{\textit{M} (\textit{SD})} & \multicolumn{2}{c}{$p$} \\ & Intercept & Slope & Intercept & Slope \\
        \midrule
        ($I_1$) Pre-teaching interval & 0.052 (0.820) & 0.085 (0.133) & .57 & $< .05$ \\
        ($I_2$) Teaching interval & 1.025 (0.690) & -0.039 (0.108) & $< .05$ & $< .05$ \\
        ($I_3$) Post-teaching interval & 0.549 (0.547) & -0.060 (0.101) & $< .05$ & $< .05$ \\
        ($I_4$) Interview interval & -0.617 (0.614) & -0.022 (0.070) & $< .05$ & $< .05$ \\
        ($I_5$) End interval & -1.004 (0.500) & -0.012 (0.074) & $< .05$ & .14 \\
        \bottomrule
    \end{tabularx}
    \caption{Analysis (\textit{M, SD, p}-values) for the mean intercepts and the mean slopes for the five intervals.}
    \label{tab_2}
\end{table}

>>>>

    postcode: "04109"

@@

    postcode: "04103"

@@

@@

    postcode: "17489" 

@@

    text: "Conceptualization, Methodology, Formal analysis, Investigation, Data Curation, Writing - Original Draft"

@@

    text: "Conceptualization, Methodology, Writing - Review & Editing, Supervision"

@@

\begin{table}[ht]
    \centering
    \begin{tabularx}{\textwidth}{lXXXXXX}
        \toprule
        Interval  & \multicolumn{2}{c}{\textit{M} (\textit{SD})} & \multicolumn{2}{c}{$p$} \\ & Intercept & Slope & Intercept & Slope \\
        \midrule
        Pre-teaching interval & 0.052 (0.820) & 0.085 (0.133) & .57 & $< .05$ ($I_1$)\\
        Teaching interval & 1.025 (0.690) & -0.039 (0.108) & $< .05$ & $< .05$ ($I_2$)\\
        Post-teaching interval & 0.549 (0.547) & -0.060 (0.101) & $< .05$ & $< .05$ ($I_3$)\\
        Interview interval & -0.617 (0.614) & -0.022 (0.070) & $< .05$ & $< .05$ ($I_4$)\\
        End interval & -1.004 (0.500) & -0.012 (0.074) & $< .05$ & .14 ($I_5$)\\
        \bottomrule
    \end{tabularx}
    \caption{Analysis (\textit{M, SD, p}-values) for the mean intercepts and the mean slopes for the five intervals.}
    \label{tab_2}
\end{table}
